{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-03 bmvc_review.tex
Intermediate editing.

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
is deployed on a low-end, embedded system.\footnote{We empirically
  come up with this computation about an 1/10th scale down of
  computational resources from a typical PC to an embedded system.}

@@

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results by the proposed method on the
  ``UAV123'' dataset. This ``UAV123'' dataset is challenging for
  object tracking as a target's scale is changed drastically with a
  few frames.}
\label{ResultsIntroduction}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, they use the MOSSE tracker to estimate a target's
translation. And then they attemped to update the scale of the target
a way where the confidence map is used to determine the scale change
between successive frames. This is based on an assumption that the
scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation, but in a more efficient
way. To be more specific, we use an ensemble of KCFs in turn, instead
of running them all together on every frame. In particular, we deploy
three KCF in turn: \textit{target}+\textit{small background}
translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
($R_{s}$) and \textit{target}+\textit{large background} translation
filter ($R_{t}^{L}$). By doing so, we could still address the scale
change and estimate target's motion efficiently while increasing
run-time performance. Figure \ref{fig:Filters} shows examples of the
ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.

\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
(a) \\
\bmvaHangBox{\includegraphics[width=10.0cm]{./figures/Workflow_EnKCF2+PF.pdf}}\\
(b)
\end{tabular}
\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker (a). It is slightly modified to handle extreme ego-motion
and we call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
\label{Workflows}
\end{figure}
The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while preserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflows}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed {\it E}nKCF for
  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
  the flexibility of the ensemble of KCFs approach we propose. The
  original {\it E}nKCF is slightly modified to track in low frame rate
  videos ($10$fps) dominated by large ego-motion. We do not integrate
  the particle filter in {\it E}nKCF2 as we test it on a temporally
  down-sampled UAV123 dataset (UAV123$\_$10fps) including sequences
  with large ego-motion on a UAV platform. Particle Filter can be
  deployed in case the camera motion is known. The run-time
  performance decreases to $150$ fps, however, ratio of the video
  frame rate and run-time performance is similar to {\it E}nKCF. The
  proposed framework can be seen in fig.~\ref{Workflows}.
\end{itemize}

@@

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Fig.~\ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
element-wise multiplication, resulting in a scale estimation in a
higher speed.
\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

After Henriques and his colleagues' presented impressive tracking 
results of KCF \cite{henriques2015high} on
VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
many variation of KCF were investigated. In particular,
\cite{ma2015long} and \cite{danelljan2014accurate} used a scale filter
to learn the target area only whereas \cite{li2014scale,
  bibi2015multi, tang2015multi} used a correlation filter learned on
the target area and its surrounding background in different size to
learn the optimal scale of the target. Our approach is particularly
similar to that of \cite{ma2015long} in that more than one KCF is used
to address the challenges of single target tracking. But ours is
different from that of \cite{ma2015long} in that we do not use those
multiple KCFs together at every frame, but alternatively at every
three frame. The way our algorithm is alternating multiple KCFs in
different goals intuitively makes sense in that the appearance of
consecutive images does not change drastically. Although it varies
based on the scene, learning a correlation filter a frame would not be
much different from the one learned using the image few or $k$ frames
later. By alternating three KCFs in turn, our algorithm runs as fast
as or faster than the original KCF. 
\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{The video frame and the learned scale correlation filters are shown next to it. 
The models in the top row correspond to the scale filter trained every frame whereas the bottom row shows the scale filter updated every $5$ frames. 
Filters updated every five frame and every frame display very large correlation.}
\label{fig:Filters_Comparison}
\end{figure}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the work-flow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. We do not have a separate pseudo-code for {\it E}nKCF2 as there are only two differences between 
  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
tracker due to large ego-motion. In the following section, we will briefly mention the theory
behind the KCF.
\begin{algorithm}[h]
\small
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{s}$ (Condition 1);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}
\begin{comment}
{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

{\it YoungWoo : What do you mean by this? Should we move it up before the EnKCF introduction? or Should we include more EnKCF-related text in it? I trimmed it further. I wanted to keep some equations because they include hyper-paramaters that is important for EnKCF.}
\end{comment}

@@

\subsection{Particle Filter for Smoothing Transition of KCFs} \label{sc:PF}
As explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential mishaps from
happening, we developed a Bayes filter that incorporates a target's
motion to smooth any outputs from the {\it E}nKCF. In particular, we
use a particle filter to estimate the target's image coordinate based
on the {\it E}nKCF's outputs. A particle filter is a sequential Monte
Carlo method that uses a finite number of particles or samples to
estimate the posterior probability density of a state of the system
\cite{thrun2005probabilistic}. In this study, the state represents a
target's pixel coordinates and its motion. In particular, the state of
the particle filter, $X_t$, is represented by $\lbrace x, y, v_{x},
v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates of the
target's centroid, $v_x$ and $v_y$ are the estimated velocity along
the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as:
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window as that of a confidence
map. Alternatively one can also use the Euclidean distance of
particles to the location of maximum response of the confidence
map. This alternative, however, would result in drifts.

>>>>

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
is deployed on a low-end, embedded system.\footnote{We empirically
  found this computation reasonable -- the computation about an 1/10th
  scale down of computational resources from a typical PC to an
  embedded system.}

@@

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results (yellow rectangles) by the
  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
  is challenging for object tracking as a target's scale is changed
  drastically in a few frames.}
\label{ResultsIntroduction}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, they use the MOSSE tracker to estimate a target's
translation. And then they attemped to update the scale of the target
a way where the confidence map is used to determine the scale change
between successive frames. This is based on an assumption that the
scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation, but in a more efficient
way. To be more specific, we use an ensemble of KCFs in turn, instead
of running them all together on every frame. In particular, we deploy
three KCF in turn: \textit{target}+\textit{small background}
translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
($R_{s}$) and \textit{target}+\textit{large background} translation
filter ($R_{t}^{L}$). By doing so, we could still address the scale
change and estimate target's motion efficiently while increasing
run-time performance. Figure \ref{fig:Filters} shows examples of the
ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$. Figure
\ref{Workflows} illustrates the work-flow of the {\it E}nKCF.

\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
(a) \\
\bmvaHangBox{\includegraphics[width=10.0cm]{./figures/Workflow_EnKCF2+PF.pdf}}\\
(b)
\end{tabular}
\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker
  (a). It is slightly modified to handle extreme ego-motion and we
  call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
\label{Workflows}
\end{figure}

The contribution of this study is a novel, single-target tracking
algorithm running a very high-speed, $\geq 300$ fps. In particular,
the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCF, in
turn, to more effectively address the scale variance and the dynamic
maneuver of a target while preserving run-time performance as high as
possible. To minimize any potential performance gap from transiting
one KCF to another, we use a Bayes filter.

@@

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Figkure \ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
element-wise multiplication, resulting in a scale estimation in a
higher speed.

\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

After Henriques and his colleagues' presented impressive tracking 
results of KCF \cite{henriques2015high} on
VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
many variation of KCF were investigated. In particular,
\cite{ma2015long} and \cite{danelljan2014accurate} used a scale filter
to learn the target area only whereas \cite{li2014scale,
  bibi2015multi, tang2015multi} used a correlation filter learned on
the target area and its surrounding background in different size to
learn the optimal scale of the target. Our approach is particularly
similar to that of \cite{ma2015long} in that more than one KCF is used
to address the challenges of single target tracking. But ours is
different from that of \cite{ma2015long} in that we do not use those
multiple KCFs together at every frame, but alternatively at every
three frame. The way our algorithm is alternating multiple KCFs in
different goals intuitively makes sense in that the appearance of
consecutive images does not change drastically. Although it varies
based on the scene, learning a correlation filter a frame would not be
much different from the one learned using the image few or $k$ frames
later. By alternating three KCFs in turn, our algorithm runs as fast
as or faster than the original KCF. 
\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{This figure shows that there is marginal difference among the
  scale filters learned either at every frame or at every 5
  frames. The sub-figures at the top row show the scale filters
  trained from every frame and those at the bottom row show the scale
  filters estimated every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the work-flow of the proposed algorithm
and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. We do not
have a separate pseudo-code for {\it E}nKCF2 as there are only two
differences between {\it E}nKCF and {\it E}nKCF2. First, the {\it
  E}nKCF2 runs $R_{t}^{L}$ every frame to better tackle large
ego-motion at low video frame rates. Second, we remove the particle
filter in the {\it E}nKCF2 tracker due to large ego-motion. In the
following section, we will briefly mention the theory behind the KCF.
\begin{algorithm}[h]
\small
	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{s}$ (Condition 1);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

@@

\subsection{Particle Filter for Smoothing Transition among KCFs} \label{sc:PF}
As explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential mishaps from
happening, we developed a Bayes filter that incorporates a target's
motion to smooth any outputs from the {\it E}nKCF. In particular, we
use a particle filter to estimate the target's image coordinate based
on the {\it E}nKCF's outputs. A particle filter is a sequential Monte
Carlo method that uses a finite number of particles or samples to
estimate the posterior probability density of a state of the system
\cite{thrun2005probabilistic}. In this study, the state represents a
target's pixel coordinates and its motion. In particular, the state of
the particle filter, $X_t$, is represented by $\lbrace x, y, v_{x},
v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates of the
target's centroid, $v_x$ and $v_y$ are the estimated velocity along
the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as:
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window as that of a confidence
map. Alternatively one can also use the Euclidean distance of
particles to the location of maximum response of the confidence
map. This alternative, however, would result in drifts.
